$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-30 paper/e6ssm-tuning-paper.tex
Fixed double equation number for superpotential, reworked comment following the superpotential definition to read better
Replaced Fig --> Fig.

      \SuperField{u}_3^c\\

@@

where the third generation Higgs fields $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and SM singlet field $\SuperField{S}_3\equiv\SuperField{S}$ 
are allowed to get VEVs. 

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
and those below;
however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
lower bound on the achievable tuning that is of interest here.}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.

>>>>

      \SuperField{u}_3^c\nonumber\\

@@

where we denote by $\SuperField{H}_d^3\equiv \SuperField{H}_d$,
$\SuperField{H}_u^3\equiv\SuperField{H}_u$ and $\SuperField{S}_3\equiv\SuperField{S}$ the third generation Higgs and SM singlet fields that are assumed to acquire non-zero VEVs.

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
and those below;
however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
lower bound on the achievable tuning that is of interest here.}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig.~\ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.
